### 2015-03-18 appendices.tex
added overall scores for case study
some more modifications and include CRI element scatterplot matrix

    Often times the SDLC contains more than the 5 basic steps of requirements, design,
    implementation, testing, and  deployment/maintenance.  Those are the high-level
    phases, but many steps are required to complete each phase.  The following list
    provides a more detailed list of what needs to be accomplished in the 
    entire life cycle of software development. These steps do not need 
    to occur in a sequential fashion.

@@

\section{CASE STUDY SOURCE CODE} 
\label{app:case}

@@

@@

>>>>

    The SDLC often contains more than the 5 basic steps of requirements, design,
    implementation, testing, and  deployment/maintenance.  Those are the high-level
    phases, but many steps are required to complete each phase.  The following list
    provides a more detailed list of what needs to be accomplished in the 
    entire life cycle of software development. These steps do not need 
    to occur in a sequential fashion.

@@

\section{CASE STUDY SOURCE CODE} 
\label{app:case}
    A full set of the source code and applicable output is available 
    at \cite{Swanstrom2015s}.

@@

    \subsection{SCHEDULE SCORES - R CODE}
        \lstinputlisting[language=R, label=src:schedule]{source/schedule.R}

@@

    \subsection{OVERALL SCORES - R CODE}
        \lstinputlisting[language=R, label=src:overall]{source/overall.R}

### 2015-03-18 paper_50_sdlc-ae.tex
some more modifications and include CRI element scatterplot matrix

    \subsection{DATABASE STRUCTURE}
        All the data necessary to compute CRI needs to be stored in a database.  This section will 
        lay out the structure of tables and relationships necessary to the store all the data
        within a relational database.  The SQL\footnote{Structured Query Language (SQL) is 
        a programming language designed for managing data in relational database 
        management system.} 
        is written for an Oracle
        database, but the scripts can be modified to work with another database
        such as: PostgreSQL, SQL Server, or MySQL.

>>>>

    \subsection{DATABASE STRUCTURE}
        All the data necessary to compute CRI needs to be stored in a database.  This section will 
        lay out the structure of tables and relationships necessary to the store all the data
        within a relational database.  The SQL\footnote{Structured Query Language (SQL) is 
        a programming language designed for managing data in relational database 
        management system.\nomenclature{SQL}{Structured Query Language}} 
        is written for an Oracle
        database, but the scripts can be modified to work with other databases
        such as: PostgreSQL, SQL Server, or MySQL.

### 2015-03-18 paper_70_case-study.tex
updates through chapter 4
some more modifications and include CRI element scatterplot matrix

    \subsection{QUALITY}
        The first step to dealing with the quality data is a quick
        analysis of the data.  Table \ref{tab:quality_desc} provides
        some descriptive statistics for the quality data.  Testing hours
        were not capture but they are optional, so the analysis can 
        continue.

@@

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/quality_plots1.png}
            \caption{QUALITY DATA PLOTS: DEPENDENT VS. INDEPENDENT VARIABLES}
            \label{fig:quality-plots1}
        \end{figure}

@@

    \subsection{AVAILABILITY}
        For the availability data,
        some descriptive statistics can be seen in 
        Table \ref{tab:availability_desc}.  The percent uptime
        was precalculated for this data so uptime, scheduled downtime,
        and unscheduled downtime are not needed.  Availability
        does not rely upon analysis of historical data since
        a known upper and lower bound exist, 1 and 0 respectively.

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/availability_scores.png}
            \caption{CRI AVAILABILITY SCORES}
            \label{fig:availability-scores}
        \end{figure}

@@

    \subsection{SCHEDULE}
        Figure \ref{tab:schedule_desc} displays some descritive statistics
        for the schedule data.  Since the data is mostly dates, the 
        descriptive statistics are limited, so extra values were
        added to the table after removing 4 outliers.  The new values
        in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
        Difference (Actual Finish - Schedule Finish), and 
        $\Delta$ ($frac{\Delta}{\text{Schedule Duration}}$ ).

@@

        Now that the distribution has been identified, the next step
        is determining the Cumulative Distribution Function (C.D.F.)
        for the distribution.  For Cauchy, the general C.D.F. is 
        given as follows.
        \[
            C.D.F. = \frac{1}{\pi}\arctan{\frac{x-x_0}{\gamma}} + \frac{1}{2}
        \]
        where 
        \begin{itemize}
            \item $x_0$ is the location
            \item $\gamma$ is the scale
        \end{itemize}

@@

        The CRI schedule scores can be seen in Figure \ref{fig:schedule-scores}.
        These scores appear more eratic than the other elements.
        This difference is due to the small number of releases every month.

@@

        Based upon the graphs for the elements scores, there does not
        appear to be any correlation.  None of the graphs
        rise and fall during the same intervals.  The missing element,
        satisfaction, is the most likely element to exhibit correlation,
        so the 4 elements analyzed here remain independent.

>>>>

    \subsection{QUALITY}
        The first step to dealing with the quality data is a quick
        analysis of the data.  Table \ref{tab:quality_desc} provides
        some descriptive statistics for the quality data.  Testing hours
        were not captured, but they are optional, so the analysis can 
        continue.

@@

            \cmidrule[0.2pt](r{0.125em}){1-1}%
            \cmidrule[0.2pt](lr{0.125em}){2-2}%
            \cmidrule[0.2pt](l{0.125em}){3-3}%
            \cmidrule[0.2pt](l{0.125em}){4-4}%
            \cmidrule[0.2pt](l{0.125em}){5-5}%
            \cmidrule[0.2pt](l{0.125em}){6-6}%
            % \midrule
            \endhead

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.25]{images/quality_plots1.png}
            \caption{QUALITY DATA PLOTS: DEPENDENT VS. INDEPENDENT VARIABLES}
            \label{fig:quality-plots1}
        \end{figure}

@@

    \subsection{AVAILABILITY}
        For the availability data,
        some descriptive statistics can be seen in 
        Table \ref{tab:availability_desc}.  The percent uptime
        was previously calculated for this data so uptime, scheduled downtime,
        and unscheduled downtime are not needed.  Availability
        does not rely upon analysis of historical data since
        a known upper and lower bound exist, 1 and 0 respectively.

        The numbers in Table \ref{tab:availability_desc} indicate
        the values are very near 1.  This is expected as SDOs
        set SLA uptime values near 1, and even strive to meet
        an uptime of 1.  An uptime of 1 means the system was
        available the entire time period.  Thus numbers for uptime
        near 1 are highly desirable for an SDO expecting
        to score well for availability.

@@

        \begin{figure}[hb]
            \centering
            \includegraphics[scale=.3]{images/availability_scores.png}
            \caption{CRI AVAILABILITY SCORES}
            \label{fig:availability-scores}
        \end{figure}

@@

    \subsection{SCHEDULE}
        Figure \ref{tab:schedule_desc} displays some descriptive statistics
        for the schedule data.  Since the data is mostly dates, the 
        descriptive statistics are limited, so extra values were
        added to the table after removing 4 outliers.  The new values
        in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
        Difference (Actual Finish - Schedule Finish), and 
        $\Delta$ ($\frac{\text{Difference}}{\text{Schedule Duration}}$ ).

@@

        Now that the distribution has been identified, the next step
        is determining the CDF
        for the distribution.  For Cauchy, the general CDF is 
        given as follows.
        \[
            CDF(x) = \frac{1}{\pi}\arctan{\frac{x-x_0}{\gamma}} + \frac{1}{2}
        \]
        where 
        \begin{itemize}
            \item $x_0$ is the location
            \item $\gamma$ is the scale
        \end{itemize}

@@

        The CRI schedule scores can be seen in Figure \ref{fig:schedule-scores}.
        These scores appear more erratic than the other elements.
        This difference is due to the small number of releases every month.

@@

        Figure \ref{fig:correlation_cri} shows a scatterplot matrix
        for the individual element scores.  No correlation appears
        to exist between any of the elements. The missing element,
        satisfaction, is the most likely element to exhibit correlation,
        so the 4 elements analyzed here remain independent.

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/correlation.png}
            \caption{SCATTERPLOT MATRIX OF CRI ELEMENT SCORES}
            \label{fig:correlation_cri}
        \end{figure}

### 2015-03-18 paper_80_conclusion.tex
some more modifications and include CRI element scatterplot matrix

    Due to the number of issues with surveys.  One area of future work would be indentifying
    a general set of questions that would best fit CRI.  This set would have to include
    the best number of questions, order of questions and wording of questions.  Therefore,
    any new organization would not have to determine their own survey, but rather just use the
    predetermined set of questions.  It would even be advantageous to build a software system to
    handle the survey distribution and collection.  Ideally, the results would automatically be
    inserted into the appropriate database tables for CRI scoring.

    As shown in Table \ref{tab:bsc}, CRI is currently not addressing 2 
    characteristics of the balanced scorecard.  If the SDO does not operate 
    on a fixed budget, CRI could be 
    expanded to include another element for financial data. The challenge arises when
    determining how to relate the SDO performance to finances.  The most likely scenario
    would be a method to either select or predicted the expected software sales
    for a month.  Then every month create an CRI element score that reflects
    how much the expected sales were exceeded or missed.  The other missing
    balanced scorecard characteristic is learning and growth.  Those are very difficult
    to quantitatively measure.  In this case some possible data points might be:
    hours of training, number of training courses, number of employees receiving
    training, number of promotions, or another measure centered around training
    courses and career growth.  Again, once data exists, the problem becomes finding
    a baseline and measuring with respect to that baseline.

    Another area of future work is the expansion of the SDLC-AE to include
    more artifacts of the SDLC.  The more artifacts and processes that can
    be collected, the deeper the understanding of the SDLC.  
    All of the data collection combined with better software analytics
    could lead to true \textit{data-driven software engineering}. Data-driven
    software engineering is the application of collecting and analyzing historical
    information about software engineering artifacts in order to
    accurately predict the outcomes of software engineering projects. This
    will lead to more informed decisions about software engineering.  Figure
    \ref{fig:sdlc-ae-adv} shows an expansion of the previous SDLC-AE diagram.  
    The new elements are in the unshaded boxes, and they are not exhaustive.
    Data-driven software engineering should 
    not to be confused with data-driven programming, in which the computer code
    describes the data instead of the sequence of opertions \cite{DDP2015}.

@@

    Currently, CRI provides a single method to evaluate past 
    performance, but it does not
    provide any guidance around making more informed future decisions. 
    Some phases are not properly tracked with the initial SDLC-AE and more
    data can be tracked for the existing phases.
    Schedules for each of the individual phases of the SDLC need to be tracked,
    not just the entire project.  Teams need to know how much time is spent
    in design versus testing.  Also, how much time is required to generate
    proper test cases?  These are just a couple of examples of expansions
    to the SDLC-AE.  These and other advancements could lead to greater
    insights about SDLC phases that are struggling and need improvement.
    The SDLC-AE could be expanded to have predictive capabilities.

@@

    Now SDOs have a technique to consistently measure performance over time.  CRI
    should help upper-level management identify the areas of the organization
    that need attention and those that do not.  CRI should save time required to 
    evaluate the performance since the result is a single number.

>>>>

    Due to the number of issues with surveys.  One area of future work would be identifying
    a general set of questions that would best fit CRI.  This set would have to include
    the best number of questions, order of questions and wording of questions.  Therefore,
    any new organization would not have to determine their own survey, but rather just use the
    predetermined set of questions.  It would even be advantageous to build a software system to
    handle the survey distribution and collection.  Ideally, the results would automatically be
    inserted into the appropriate database tables for CRI scoring.

    As shown in Table \ref{tab:bsc}, CRI is currently not addressing 2 
    characteristics of the balanced scorecard.  If the SDO does not operate 
    on a fixed budget, CRI could be 
    expanded to include another element for financial data. The challenge arises when
    determining how to relate the SDO performance to finances.  The most likely scenario
    would be a method to either select or predict the expected software sales
    for a month.  Then every month create an CRI element score that reflects
    how much the expected sales were exceeded or missed.  The other missing
    balanced scorecard characteristic is learning and growth.  These are very difficult
    to quantitatively measure.  In this case some possible data points might be:
    hours of training, number of training courses, number of employees receiving
    training, number of promotions, or another measure centered around training
    courses and career growth.  Again, once data exists, the problem becomes finding
    a baseline and measuring with respect to that baseline.

    Another area of future work is the expansion of the SDLC-AE to include
    more artifacts of the SDLC.  The more artifacts and processes that can
    be collected, the deeper the understanding of the SDLC.  
    All of the data collection combined with better software analytics
    could lead to true \textit{data-driven software engineering}. Data-driven
    software engineering is the application of collecting and analyzing historical
    information about software engineering artifacts in order to
    accurately predict the outcomes of software engineering projects. This
    will lead to more informed decisions about software engineering.  Figure
    \ref{fig:sdlc-ae-adv} shows an expansion of the previous SDLC-AE diagram.  
    The new elements are in the unshaded boxes, and they are not exhaustive.
    Data-driven software engineering should 
    not to be confused with data-driven programming, in which the computer code
    describes the data instead of the sequence of operations \cite{DDP2015}.

@@

    Currently, CRI provides a single method to evaluate past 
    performance, but it does not
    provide any guidance around making more informed future decisions. 
    Some phases are not properly tracked with the initial SDLC-AE and more
    data can be tracked for the existing phases.
    Schedules for each of the individual phases of the SDLC need to be tracked,
    not just the entire project.  Teams need to know how much time is spent
    in design versus testing.  Consideration should also be given to the amount
    of time required to generate
    proper test cases.  These are just a couple of examples of expansions
    to the SDLC-AE.  These and other advancements could lead to greater
    insights about SDLC phases that are struggling and need improvement.
    The SDLC-AE could be expanded to have predictive capabilities.

@@

    Now SDOs have a technique to consistently measure performance over time.  CRI
    will help upper-level management identify the areas of the organization
    that need attention and those that do not.  CRI will save time required to 
    evaluate performance since the result is a single number.
